### 2012-12-29 manuscript.tex
a meio caminha dos resultados

 \begin{equation}\label{eq:eff1}
  \eta=\frac{bits\, alocated-bits\, used}{bits\,alocated}
 \end{equation}
 \subsubsection*{Method 1}
 Let $M_{r \times c}$ be the matrix we wish to compress. we can define the efficiency of the compression as:

Equation \ref{eq:eff1} represent the compression ratio achieved by the method. In comparison with a conventional allocation (64-bit integers) we can rewrite equation \ref{eq:eff1} as:

\begin{align}\label{eq:22}
 \eta_1 &= \frac{64 \times rc - b(max M) \times rc}{64 \times rc}\nonumber\\
 &= \frac{64  - b }{64}
\end{align}

As we can see in (\ref{eq:22}), $\eta_1$ does not depend on size of the matrix, only on the bit-length of $\max M$ (equation \ref{eq:19}). According to equation \ref{eq:22} if $b(\max M)=64$, $\eta_1$ will be 0, i.e. no compression is possible. This leads to a very interesting optimization oportunity: divide the entire matrix by the greatest common divisor  of its elements. On the other extreme, if the matrix is composed exclusively of 0s and 1s, maximal compression is achievable, $\eta_1=1$.

\begin{equation} \label{eq:19}
 0000000000000000000000000000000000\underbrace{1111111111}_{1023}\underbrace{\overbrace{000000000}^{\text{Wasted}}1}_{1}\underbrace{\overbrace{000000000}^{\text{Wasted}}0}_{0}
\end{equation}

\begin{figure}[h]
 \centering
 \psfrag{e}{$\xi$}
 \includegraphics[scale=0.5]{fig01}
 \caption{Compression efficiency of method 1 behavior with respect to bit number.}
 \label{fig:01}
\end{figure}

 \subsubsection*{Method 2}

 For the second method, compression depends on the value of each element of the matrix. Thus to compute its efficiency, we shal modify equation \ref{eq:eff1}. We'll start by grouping the elements by bit length, since in this method, bit-lentgh variability greatly affects the compression ratio.

Again consider the matrix $M_{r \times c}$, only the $rc$ elements are now divided into $g$ groups, with $f_i$ numbers of bit-length $b_i = b(m_i)$ each. Let $k = b(b(\max M))$, i.e., the bit length of the bit-length of $\max M$. The efficiency $\eta_2$ is then defined as shown in \ref{eq:24}. Equation \ref{eq:20} can help us visualize it.

\begin{equation} \label{eq:20}
 0000000000000000000000000000000000000000\underbrace{1111111111}_{1023}\underbrace{1010}_{10}\underbrace{1}_{1}\underbrace{0001}_{1}\underbrace{0}_{0}\underbrace{0001}_{1}
\end{equation}

@@

Consider a matrix $M$ such that $m_{i,j} \in \mathbb{Z}$. In this section we will examine and compare the efficiency of the two compression methods described.

Since the efficiency of both methods depend on the distribution of the bit lengths $b(m_{i,j})$, we will explore a variety of distributions and try to cover the most common cases.

For simplicity we will model the distribution of  as a mixture $X$ of two Beta distributions ,$ B_1 \sim Beta(\alpha_1,\beta_1)$ and $B_2 \sim Beta(\alpha_2,\beta_2)$, whose probability function is shown in equation (eq.\ref{eq:mixture}). Since the Beta distribution is defined only in the interval $[0,1] \subset \mathbb{R}$ , we applied a simple transformation (\ref{eq:transf}) to the mixture in order to map it to the interval of $[1,64] \subset \mathbb{Z}$

@@

\begin{equation}\label{eq:transf}
   \lfloor 64 \times x \rfloor + 1
\end{equation}

@@

Given any matrix generated by our mixture distribution, we can use equation \ref{eq:22} and \ref{eq:25}, to determine the compression efficiency of methods 1 and 2, respectively.

With $w=0$, ie, our mixture is reduce to a single Beta distribution. In Figure \ref{fig:02},
we show some distributions of bit-lengths for some combinations of $\alpha_1$ and $\beta_1$. From the figure it can be seen that we can generate just about any kind of unimodal distributions in the interval $[1,64]$.

@@

As we are sampling the from set of all possible distributions of bit-length, represented byt the mixture of betas presented above, in order to make our results more general, we will base our analysis on the expected bit-length of a sample, since the efficiency of both methods  depend on it. So, from equations \ref{eq:22} and \ref{eq:25}, the expected efficiencies become:

>>>>

 \begin{equation}\label{eq:eff1}
  \eta=\frac{bits\, alocated-bits\, used}{bits\,alocated}
 \end{equation}

 Where \textit{bits alocated} above mean total bits required for standard storage of the matrix, without compression, while bits used mean total bits requires to store the matrix after compression.
 \subsubsection*{SM Method}
 Let $M_{r \times c}$ be the matrix we wish to compress. In comparison with a conventional allocation (64-bit integers) we can apply equation \ref{eq:eff1} to caluculate the efficiency of the SM method:

\begin{align}\label{eq:22}
 \eta_1 &= \frac{64 \times rc - b(max M) \times rc}{64 \times rc}\nonumber\\
 &= \frac{64  - b(max M) }{64}
\end{align}

As we see in \ref{eq:22}, $\eta_1$ does not depend on size of the matrix, only on the bit-length of $\max M$. If $b(\max M)=64$, $\eta_1$ is 0, i. e. no compression is possible. On the other extreme, if the matrix is composed exclusively of 0s and 1s, maximal compression is achievable, $\eta_1=1$.

 \subsubsection*{VLB Method}

 For the VLB method, compression depends on the value of each element of the matrix. In this method bit-lentgh variability affects the compression ratio, so the formula will have to include this information.

Let the $rc$ elements of the matrix $M_{r \times c}$ be divided into $g$ groups, each with $f_i$ numbers of bit-length $b_i = b(m_i)$. Thus $f_i$ is the frequency of each bit-length present in $M$. Let $k = b(b(\max M))$, i.e., the bit length of the bit-length of $\max M$. The efficiency $\eta_2$ is shown below.

@@

\paragraph{Random Matrix Generation.}
In both methods, compression eficiency depends on the distribution of the bit-lengths $b(m_{i,j})$. Thus, in this section, a method to generate a variety of random bit-length distributions is proposed.

For simplicity we will model the distribution of  as a mixture $X$ of two Beta distributions ,$ B_1 \sim Beta(\alpha_1,\beta_1)$ and $B_2 \sim Beta(\alpha_2,\beta_2)$, whose probability function is shown in equation (eq.\ref{eq:mixture}). Since the Beta distribution is defined only in the interval $[0,1] \subset \mathbb{R}$ , we applied a simple transformation ($\lfloor 64 \times x \rfloor + 1$) to the mixture in order to map it to the interval of $[1,64] \subset \mathbb{Z}$

@@

@@

From now on we will apply equations \ref{eq:22} and \ref{eq:25}, to determine the compression efficiency of methods SM and VLB for random matrices generated as describe above.

With $w=0$, a single Beta distribution is used. In Figure \ref{fig:02},
we show some distributions of bit-lengths for some combinations of $\alpha_1$ and $\beta_1$. From the figure it can be seen that a large variety of unimodal distributions can be generated in the interval $[1,64]$.

@@

As we are sampling the from set of all possible distributions of bit-length, represented by the mixture of betas presented above, in order to make our results more general, we will base our analysis on the expected bit-length of a sample, since the efficiency of both methods  depend on it. So, from equations \ref{eq:22} and \ref{eq:25}, the expected efficiencies become:
